A Temporal Logic Based Framework for Intrusion Detection

### 2023-09-02 Paper/main.tex
update

\textbf{Semantics.} First of all two assumptions are important:\begin{enumerate}
    \item There is a finite sequence of occurrences called $\sigma$ that is a merge of the system registered logs organized by ascending time. An example of event could be the following: 
    \begin{align*}
        & \text{LoginLogoutEvent}\{userId:\ \underline{\text{string}},action:\ \underline{\text{int}}, userId:\ \time{\text{double}}\} 
    \end{align*}
\end{enumerate}

>>>>

\textbf{Semantics.} First of all two assumptions are important:\begin{enumerate}
    \item There is a finite sequence of occurrences called $\sigma=\alpha_{1},\ldots ,\alpha_{n}$ that is a merge of the system registered logs organized by ascending time. 
    The structure of an event record $\alpha_i$ is the following:
    \begin{align*}
        & \text{LoginLogoutEvent}\{userId:\underline{\text{string}},action: \underline{\text{int}}, time: \underline{\text{double}}\} 
    \end{align*}
    An example of event could be: $\{userId:\text{"Lorenzo"},action:\text{login},time:\text{20}\}$
\end{enumerate}
